---
title: "Density Map of COVID-19 Related Visits to EMS Hopitals in the State of Illinois"
date: "4/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE,warning=FALSE, include=FALSE}
#import the dataset
library(stringr)
data <- read.csv("hospital_zip.csv")
```

```{r,echo=FALSE,warning=FALSE, include=FALSE}
#Parse out zipcode and frequency for each month

#January
data$X2020.01 <- as.character(data$X2020.01)
data$janzip <- substring(data$X2020.01,1,5)
data$janfreqtemp<- substring(data$X2020.01,8,12)
data$jannchar <- nchar(data$janfreqtemp)

for (i in 1:length(data$jannchar)) {
  
  if (data$jannchar[i]==5) {data$janfreq[i] <- substring(data$janfreqtemp[i], 1,4)}
  
  else if (data$jannchar[i]==4) {data$janfreq[i] <- substring(data$janfreqtemp[i], 1,3)}
  
  else if (data$jannchar[i]==3) {data$janfreq[i] <- substring(data$janfreqtemp[i], 1,2)}
  
  else if (data$jannchar[i]==2) {data$janfreq[i] <- substring(data$janfreqtemp[i], 1,1)}
  
}

data$janfreq<- as.numeric(data$janfreq)
```

```{r,echo=FALSE,warning=FALSE, include=FALSE}
#Feburary 
data$X2020.02 <- as.character(data$X2020.02)
data$febzip <- substring(data$X2020.02,1,5)
data$febfreqtemp<- substring(data$X2020.02,8,12)
data$febnchar <- nchar(data$febfreqtemp)

for (i in 1:length(data$febnchar)) {
  
  if (data$febnchar[i]==5) {data$febfreq[i] <- substring(data$febfreqtemp[i], 1,4)}
  
  else if (data$febnchar[i]==4) {data$febfreq[i] <- substring(data$febfreqtemp[i], 1,3)}
  
  else if (data$febnchar[i]==3) {data$febfreq[i] <- substring(data$febfreqtemp[i], 1,2)}
  
  else if (data$febnchar[i]==2) {data$febfreq[i] <- substring(data$febfreqtemp[i], 1,1)}
  
}

data$febfreq<- as.numeric(data$febfreq)

```

```{r,echo=FALSE,warning=FALSE, include=FALSE}
#Drop the temporary columns we created
datajan<-subset(data, select = -c(X2020.01, X2020.02,janfreqtemp, jannchar,febfreqtemp, febnchar,febzip, febfreq ))
datafeb<-subset(data, select = -c(X2020.01, X2020.02,janfreqtemp, jannchar,febfreqtemp, febnchar,janzip, janfreq ))
```


```{r,echo=FALSE,warning=FALSE, include=FALSE}
#Import dataset that matches zipcodes to latitude and longtitude 
library(data.table)
zip <- fread('https://gist.githubusercontent.com/erichurst/7882666/raw/5bdc46db47d9515269ab12ed6fb2850377fd869e/US%2520Zip%2520Codes%2520from%25202013%2520Government%2520Data')
```

```{r,echo=FALSE,warning=FALSE, include=FALSE}
#Merge this file with the hospital zipcode for Janurary 
colnames(zip) <- c("janzip", "lat", "long")
datajan <- merge(datajan, zip, on=janzip, how=inner)
#Excluding this one zipcode that is outside of IL
datajan<- datajan[datajan$janzip !="59601",]
```

```{r,echo=FALSE,warning=FALSE, include=FALSE}
#Merge this file with the hospital zipcode for Feburary
colnames(zip) <- c("febzip", "lat", "long")
datafeb <- merge(datafeb, zip, on=febzip, how=inner)
datafeb <- datafeb[datafeb$febzip !="23234",]

```


```{r,echo=FALSE,warning=FALSE, include=FALSE}
library(dplyr)
library(maptools)
library(ggmap)
library(ggplot2)
library(ggthemes)
library(viridis)

#Plot the base map of IL with county borders 
states <- map_data("state")
IL <- subset(states, region %in% c("illinois"))

counties <- map_data("county")
IL_county <- subset(counties, region == "illinois")

il_base <- ggplot(data = IL, mapping = aes(x = long, y = lat, group=group)) + 
  coord_fixed(1.5) + 
  geom_polygon(color = "black", fill = NA) +theme_map()
```

#### Key Takeaways:
1. Visits to hospitals were mostly clustered in urban areas in the Northeastern region of Illinois (EMS 7-11) in both Janurary and Feburary. 

2. Outside of the urban areas, visits to hospitals were also high (visits > 1500) in the following counties in both Janurary and Feburary: Stephenson, Adams, Tazewell, Fraklin, and Vermillion

<br />

#### Density Map of Visits to EMS Hopitals in IL in January 
```{r,echo=FALSE,warning=FALSE}

#Plot the second layer of map that shows the number of visits to EMS Hospitals in Janurary 
ggplot() + coord_fixed(1.4) + 
  geom_polygon(data = IL,  aes(x = long, y = lat, group=group), color = "black", fill = NA) +
  geom_polygon(data = IL_county, aes(x = long, y = lat,group=group),fill = NA, color = "black")+
  geom_point(data=datajan,aes(x=long, y=lat,size=janfreq, color=janfreq), alpha=1)+
  scale_color_gradient2(low="burlywood", mid="gold1", high="firebrick")+
  labs(color= "Visit Frequency", size="Visit Frequency")+
  theme_map()+  
  scale_size(range = c(0, 4))+
  theme(legend.position="bottom")
```

#### Density Map of Visits to EMS Hopitals in IL in Feburary 
```{r,echo=FALSE,warning=FALSE}
#Plot the second layer of map that shows the number of visits to EMS Hospitals in Feburary

ggplot() + coord_fixed(1.4) + 
  geom_polygon(data = IL,  aes(x = long, y = lat, group=group), color = "black", fill = NA) +
  geom_polygon(data = IL_county, aes(x = long, y = lat,group=group),fill = NA, color = "black")+
  geom_point(data=datafeb,aes(x=long, y=lat,size=febfreq, color=febfreq), alpha=1)+
  scale_color_gradient2(low="burlywood", mid="gold1", high="firebrick")+
  labs(color= "Visit Frequency", size="Visit Frequency")+
  theme_map()+
  scale_size(range = c(0, 4))+
  theme(legend.position="bottom")
```


