---
title: "Mobility Trends by EMS Regions"
date: "4/8/2020"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,echo=FALSE,include=FALSE}
#Loading the csv file 
library(dplyr)
library(stringr)
data <- read.csv("Mobility_Trend_EMS.csv")
```


```{r,echo=FALSE,include=FALSE}
colnames(data) <- c("EMS","County", "Retail/Recreation (%)", "Grocery/Pharmacy (%)", "Parks (%)", "Transit Stations (%)", "Workplace (%)", "Residential (%)")
head(data)
```

These reports show how visits and length of stay at different places change on compared to a baseline in each EMS region in the State of Illinois. Changes for each day are compared to a baseline value for that day of the week. The baseline is the median value, for the corresponding day of the week, during the 5- week period Jan 3–Feb 6, 2020. Data was extracted on March 29th, 2020. 

###Mobility Change by EMS Region
```{r,echo=FALSE, warning=FALSE}
#Summarize by EMS Region
knitr::kable(data %>% subset(select=c("EMS", "Retail/Recreation (%)", "Grocery/Pharmacy (%)", "Parks (%)", "Transit Stations (%)", "Workplace (%)", "Residential (%)"))%>% group_by(EMS)  %>% summarise_at(vars(c("Retail/Recreation (%)", "Grocery/Pharmacy (%)", "Parks (%)", "Transit Stations (%)", "Workplace (%)", "Residential (%)")), funs(mean(., na.rm=TRUE))) %>% round(digit=2))

```


```{r,echo=FALSE, warning=FALSE,include=FALSE}
library(ggplot2)
new_data<- data %>% subset(select=c("EMS", "Retail/Recreation (%)", "Grocery/Pharmacy (%)", "Parks (%)", "Transit Stations (%)", "Workplace (%)", "Residential (%)"))%>% group_by(EMS)  %>% summarise_at(vars(c("Retail/Recreation (%)", "Grocery/Pharmacy (%)", "Parks (%)", "Transit Stations (%)", "Workplace (%)", "Residential (%)")), funs(mean(., na.rm=TRUE))) %>% round(digit=2)
new_data <- as.data.frame(new_data)
new_data$EMS <-as.factor(new_data$EMS)
```


```{r,echo=FALSE,warning=FALSE,include=FALSE}
#retail
library(RColorBrewer)
library(gridExtra)
library(ggpubr)
retail <-ggplot(new_data, aes(x=EMS, y=new_data[,2],fill=EMS)) + geom_bar(stat="identity") +
theme_bw()+
scale_x_discrete(labels=c("1", "2", "3","4", "5", "6", "7", "8", "9", "10", "11"))+
scale_fill_brewer(palette = "Spectral")+
ylab("")+ggtitle("Retail/Recreation (%)")+
xlab("")+
theme(plot.title = element_text(hjust = 0.5))+
ylim(c(-65,65))+guides(fill=FALSE)

#grocery
grocery <- ggplot(new_data, aes(x=EMS, y=new_data[,3],fill=EMS)) + geom_bar(stat="identity") +
theme_bw()+
scale_x_discrete(labels=c("1", "2", "3","4", "5", "6", "7", "8", "9", "10", "11"))+
scale_fill_brewer(palette = "Spectral")+
ylab("")+ggtitle("Grocery/Pharmacy (%)")+
xlab("")+
theme(plot.title = element_text(hjust = 0.5))+
ylim(c(-65,65))+guides(fill=FALSE)

#parks
parks <- ggplot(new_data, aes(x=EMS, y=new_data[,4],fill=EMS)) + geom_bar(stat="identity") +
theme_bw()+
scale_x_discrete(labels=c("1", "2", "3","4", "5", "6", "7", "8", "9", "10", "11"))+
scale_fill_brewer(palette = "Spectral")+
ylab("")+ggtitle("Parks (%)")+
xlab("")+
theme(plot.title = element_text(hjust = 0.5))+
ylim(c(-65,65))+guides(fill=FALSE)

#transit
transit <- ggplot(new_data, aes(x=EMS, y=new_data[,5],fill=EMS)) + geom_bar(stat="identity") +
theme_bw()+
scale_x_discrete(labels=c("1", "2", "3","4", "5", "6", "7", "8", "9", "10", "11"))+
scale_fill_brewer(palette = "Spectral")+
ylab("")+ ggtitle("Transit Stations (%)")+
xlab("")+
theme(plot.title = element_text(hjust = 0.5))+
ylim(c(-65,65))+guides(fill=FALSE)

#Workplace
workplace <- ggplot(new_data, aes(x=EMS, y=new_data[,6],fill=EMS)) + geom_bar(stat="identity") +
theme_bw()+
scale_x_discrete(labels=c("1", "2", "3","4", "5", "6", "7", "8", "9", "10", "11"))+
scale_fill_brewer(palette = "Spectral")+
ylab("")+ ggtitle("Workplace (%)")+
xlab("EMS Regions")+
theme(plot.title = element_text(hjust = 0.5))+
ylim(c(-65,65))+
  guides(fill=FALSE)

#Residential
residential <- ggplot(new_data, aes(x=EMS, y=new_data[,7],fill=EMS)) + geom_bar(stat="identity") +
theme_bw()+
scale_x_discrete(labels=c("1", "2", "3","4", "5", "6", "7", "8", "9", "10", "11"))+
scale_fill_brewer(palette = "Spectral")+
ylab("")+
ggtitle("Residential (%)")+
xlab("")+
theme(plot.title = element_text(hjust = 0.5))+
ylim(c(-65,65))+
guides(fill=FALSE)


```

###Mobility Change by EMS Region and Public Location
```{r,echo=FALSE,warning=FALSE}
figure <- ggarrange(retail, grocery, parks, transit, workplace,residential, nrow=2, ncol=3,common.legend = TRUE,legend="bottom")
figure
```