---
title: "IDPH Data EDA Visualizations"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = '/Users/Excenity/Documents/CHiP-LOCAL/COVID/IDPH_Data/Output/Graphs/')

library(data.table)
library(Amelia)
library(lubridate)
library(tidyverse)
library(ggplot2)

df = fread('/Users/Excenity/Documents/CHiP-LOCAL/COVID/IDPH_Data/Output/Cleaned_Data/idph_cleaned_dates.csv')

nyt_df = fread('/Users/Excenity/Documents/CHiP-LOCAL/COVID/NYT Data/nyt_data_by_day_county.csv')
```


### Data Cleaning 
1. Convert to date formats
2. Change age category names for under 21
3. Make sure patients that are in ICU or ventilators are hospitalized

```{r echo=FALSE, message=FALSE, warning=FALSE}
df$spec_date = as.Date(df$spec_date)
df$admission_date = as.Date(df$admission_date)
df$onset_date = as.Date(df$onset_date)

df$date_diff = as.numeric(df$admission_date - df$onset_date)
```

```{r}
# cleaning
df$sex[is.na(df$sex)] = 'Unknown'

df$age[df$age == 'Under 21'] = '0-20'

# hopsitalized cleaning
df$hospital_admission[df$icu == 'Yes'] = 'Yes'  
df$hospital_admission[df$ventilator == 'Yes'] = 'Yes'
```

### Case and Hospitalizations 
1. Cases are census numbers of patients in the dataset - Aggregated by date
2. Hopsitalized are census numbers of hospitalized patients in the dataset - Aggregated by date

```{r echo=FALSE, message=FALSE, warning=FALSE}
graph_census = function(df, title, file_name)
{
  df_time = as.data.frame(df %>% group_by(spec_date) %>% count() %>% arrange(spec_date))
  df_time = df_time %>% mutate(cum_count = cumsum(n)) %>% filter(!is.na(spec_date))
  
  df_time_hos = df %>% filter(hospital_admission == 'Yes') 
  df_time_hos = as.data.frame(df_time_hos %>% group_by(spec_date) %>% count() %>% arrange(spec_date))
  df_time_hos = df_time_hos %>% mutate(cum_count_hos = cumsum(n)) %>% filter(!is.na(spec_date))
  
  ggplot(df_time, aes(x = spec_date, y = cum_count, fill = 'orange')) + geom_area(alpha = .5) +
    geom_line(alpha = .9, color = 'orange') +
    geom_area(data = df_time_hos, aes(x = spec_date, y = cum_count_hos, fill = 'red'), alpha = .5) +
    geom_line(data = df_time_hos, aes(x = spec_date, y = cum_count_hos), color = 'red', alpha = .9) +
    scale_fill_manual(values = c('orange', 'red'), name = 'Counts',
                      labels = c('Cases Census', 'Hosptialization Census')) +
    ggtitle(title) + theme_bw() + xlab('Onset Date') + ylab('Number of Cases') +
    theme(text = element_text(family = 'Avenir')) + ggsave(file_name)
}
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# daily census (cases, hopsitalizations)
graph_census(df, 'Total Census', '1-Total Census.png')

# without travel history
graph_census(df %>% filter(travel == 'No'), 'Census W/O Travel History', '2-Census without Travel.png')
```

##### Cook County
Same graphs for Cook County

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
# Daily Census 
graph_census(df %>% filter(county == 'Cook'), 'Total Census - Cook County', 'cook1-Total Census.png')

# without travel history
graph_census(df %>% filter(county == 'Cook' & travel == 'No'), 'Census W/O Travel History - Cook County',
             'cook2-Census without Travel.png')
```

### Demographics Comparison b/w Hospitalized and Non-Hospitalized
1. Distribution of Gender of Patients
2. Distribution of Gender of Patients breakdown by Hospitalization Status
3. Distribution of Age of Patients
4. Distribution of Age of Patients breakdown by Hospitalization Status
```{r echo=FALSE, message=FALSE, warning=FALSE}
df_demo = df
df_demo$hospital_admission[is.na(df_demo$hospital_admission)] = 'Unknown'
df_demo$hospital_admission = factor(df_demo$hospital_admission, levels = c('No', 'Yes', 'Unknown'))

# gender
ggplot(df_demo, aes(x = sex)) + geom_histogram(alpha = .75, stat= 'count') +  ggtitle('Gender Distribution') +
  theme_bw() + theme(text = element_text(family = 'Avenir')) + ggsave('3-Gender Distribution.png')
ggplot(df_demo, aes(x = sex, fill = hospital_admission)) + 
  geom_histogram(position = 'dodge', stat = 'count', alpha = .75) +  ggtitle('Gender Distribution By Admissions') +
  theme_bw() + theme(text = element_text(family = 'Avenir')) + scale_fill_discrete(name = 'Admitted to Hospital?') +
  ggsave('8-Gender Distribution By Admissions.png')

# age group
df_demo$age[df_demo$age == 'Under 21'] = '0-20'
ggplot(df_demo, aes(x = age)) + geom_histogram(alpha = .75, stat= 'count') +  ggtitle('Age Distribution') +
  theme_bw() + theme(text = element_text(family = 'Avenir')) + ggsave('4-Age Distribution.png')
ggplot(df_demo, aes(x = age, fill = hospital_admission)) +
  geom_histogram(position = 'dodge', stat = 'count', alpha = .75) + ggtitle('Age Distribution By Admissions') +
  theme_bw() + theme(text = element_text(family = 'Avenir')) + scale_fill_discrete(name = 'Admitted to Hospital?') + 
  ggsave('9-Age Distribution By Admissions.png')
```

### Days b/w Onset and Hospitalizations
1. Distribution of difference between onset date and hospitalized dates. Records with missing dates were removed (Histogram + Density Plot)
2. Distribution of difference between onset date and hospitalized dates breakdown by Gender. Records with missing dates were removed (Histogram + Density Plot) 
3. Distribution of difference between onset date and hospitalized dates breakdown by Age Group Records with missing dates were removed (Boxplot) 
```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(df %>% filter(!is.na(date_diff) & date_diff >= 0), aes(x = date_diff)) +
  geom_histogram(aes(y = ..density..), alpha = .5, binwidth = .8, color = 'white', bins = 41) +
  geom_density(aes(x = date_diff), alpha = .2, fill = 'green', color = 'dark green') + 
  scale_y_continuous(name = 'Density', labels = scales::percent) + theme_bw() +
  xlab('Days') + ylab('Count') + ggtitle('Distribution Between Onset and Hospitalization') + 
  theme(text = element_text(family = 'Avenir')) + ggsave('5-Day Difference Onset Admission.png')

# broken down by sex 
ggplot(df %>% filter(!is.na(date_diff) & date_diff >= 0), aes(x = date_diff, color = sex, fill = sex)) +
  geom_histogram(aes(y = ..density..), alpha = .5, position = 'dodge', bins = 41) +
  geom_density(aes(x = date_diff), alpha = .2) + 
  scale_y_continuous(name = 'Density', labels = scales::percent) + theme_bw() +
  xlab('Days') + ylab('Count') + ggtitle('Distribution Between Onset and Hospitalization') + 
  theme(text = element_text(family = 'Avenir')) + ggsave('6-Day Difference Onset Admission Gender.png')

# broken down by age
df$age[df$age == 'Under 21'] = '0-20'
ggplot(df %>% filter(!is.na(date_diff) & date_diff >= 0), aes(x = age, y = date_diff, color = age)) +
  geom_boxplot(alpha = .85) + theme_bw() +
  xlab('Age') + ylab('Date Difference') + ggtitle('Distribution Between Onset and Hospitalization') +
  theme(text = element_text(family = 'Avenir')) + ggsave('7-Day Difference Age.png')
```

### Additional Breakdown
Histograms of patients' testing reasons, travel history, ventilator use, in ICU

```{r echo=FALSE, message=FALSE, warning=FALSE} 
# Testing Reason
df_testing = df
df_testing$testing_reason[is.na(df_testing$testing_reason)] = 'Unknown'
ggplot(df_testing %>% filter(!is.na(testing_reason)), aes(x = testing_reason)) +
  geom_histogram(stat = 'count', alpha = .75) + coord_flip() + theme_bw() + xlab('Count') + ylab('Testing Reason') + 
  ggtitle('Testing Reason Breakdown') + theme(text = element_text(family = 'Avenir')) +
  ggsave('10-Testing Reason Breakdown.png')

# Travel 
df$travel[is.na(df$travel)] = 'Unknown'
df$travel = factor(df$travel, levels = c('Unknown', 'Yes', 'No'))
ggplot(df %>% filter(!is.na(travel)), aes(x = travel)) + geom_histogram(stat = 'count', alpha = .75) + coord_flip() +
  xlab('Count') + ylab('Travel') + ggtitle('Travel Breakdown') + theme(text = element_text(family = 'Avenir')) + 
  ggsave('11-Travel Breakdown.png')

# ventilator
df$ventilator[is.na(df$ventilator)] = 'Unknown'
df$ventilator = factor(df$ventilator, levels = c('Unknown', 'Yes', 'No'))
ggplot(df %>% filter(!is.na(ventilator)), aes(x = ventilator)) + geom_histogram(stat = 'count', alpha = .75) +
  coord_flip() + xlab('Count') + ylab('Ventilator') + ggtitle('Ventilator Use Breakdown') + ggsave('12-Ventilator Breakdown.png')
 
# ICU
df$icu[is.na(df$icu)] = 'Unknown'
df$icu = factor(df$icu, levels = c('Unknown', 'Yes', 'No'))
ggplot(df %>% filter(!is.na(icu)), aes(x = icu)) + geom_histogram(stat = 'count', alpha = .75) +
  coord_flip() + xlab('Count') + ylab('ICU Usage') + ggtitle('ICU Usage Breakdown') + 
  theme(text = element_text(family = 'Avenir')) + ggsave('13-ICU Breakdown.png')
```

### Age Distribution By All, Hospitalization, ICU, Vent
1. Distribution of age groups in patients with different resource utilization statuses 
2. In each category, only patients that qualify for status is present

```{r echo=FALSE, message=FALSE, warning=FALSE}
all = df %>% group_by(age) %>% count()
all$category = 'Total'
hospitalized = df %>% filter(hospital_admission == 'Yes') %>% group_by(age) %>% count()
hospitalized$category = 'Hospitalized'
icu = df %>% filter(icu == 'Yes') %>% group_by(age) %>% count()
icu$category = 'In ICU'
vent = df %>% filter(ventilator == 'Yes') %>% group_by(age) %>% count()
vent$category = 'On Ventilator'

final = rbind(all, hospitalized)
final = rbind(final, icu)
final = rbind(final, vent)
final = final %>% filter(age != '#N/A')

ggplot(final, aes(x = age, y = n, fill = category)) + geom_bar(alpha = .75, stat = 'identity') + xlab('Age Group') +
  ylab('Count') + ggtitle('Age Breakdown by Patient Category') +
  theme(text = element_text(family = 'Avenir')) + scale_fill_discrete(name = 'Category') + 
  theme_bw() + facet_wrap(~ category, scales = 'free') #+ 
  #ggsave('14-Age Distribution by Category.png', width = 10, height = 10)
```

### Age Distribution Hospitalization, ICU, Vent
1. Each category is filtered by the previous category 
  1. Hospitalized category denominator is all patients count
  2. ICU category denominator is hospitalized patients count
  3. Ventilator category denominator is ICU patients count
2. Histogram (percentage) of yes and no categories by age group
3. Density plot of yes and no categories by age group
```{r echo=FALSE, message=FALSE, warning=FALSE}
all = df %>% select(ID, age, hospital_admission, icu, ventilator)
names(all)[3:5] = c('Hospital Admission', 'In ICU', 'On Ventilator')
all[is.na(all)] = 'Unknown'

all = all %>% gather(key = 'category', value = 'Legend', 'Hospital Admission', 'In ICU', 'On Ventilator')
all$Legend = as.factor(all$Legend)
all$category = as.factor(all$category)
all$age = as.factor(all$age)
all$age_cat = as.numeric(all$age)

unknown_count = all %>% filter(Legend == 'Unknown') %>% group_by(category) %>% count()
# cleaning 
all = all %>% filter(age !='#N/A' & Legend != 'Unknown')
all_line = all

# breakdown by hospitalization
hos_total = all %>% filter(category == 'Hospital Admission') %>% group_by(category, Legend) %>% count()
names(hos_total)[3] = 'total'
hos_counts = all %>% filter(category == 'Hospital Admission') %>% group_by(age, category, Legend) %>% count() 
hos_counts = inner_join(hos_total, hos_counts)

# breakdown by ICU 
hospitalized_list = all %>% filter(category == 'Hospital Admission' & Legend == 'Yes') %>% distinct(ID)
icu_total = all %>% filter(ID %in% hospitalized_list$ID & category == 'In ICU') %>% group_by(category, Legend) %>% count()
icu_counts = all %>% filter(ID %in% hospitalized_list$ID & category == 'In ICU') %>% group_by(age, category, Legend) %>% count()
names(icu_total)[3] = 'total'
icu_counts = inner_join(icu_total, icu_counts)

# breakdown by Ventilator
ICU_list = all %>% filter(category == 'In ICU' & Legend == 'Yes') %>% distinct(ID)
vent_total = all %>% filter(ID %in% ICU_list$ID & category == 'On Ventilator') %>% group_by(category, Legend) %>% count()
vent_counts = all %>% filter(ID %in% ICU_list$ID & category == 'On Ventilator') %>% group_by(age, category, Legend) %>% count()
names(vent_total)[3] = 'total'
vent_counts = inner_join(vent_total, vent_counts)

all = rbind(hos_counts, icu_counts)
all = rbind(all, vent_counts)

all$percentage = all$n / all$total

graph_caption = 'ICU and Ventilator Categories only contain patients that are hospitalized. All Unknowns were removed.'

ggplot() + geom_bar(data = all, aes(x = age, y = percentage, fill = Legend), alpha= .5, stat = 'identity', position = 'dodge') +
  geom_text(data = all %>% filter(Legend == 'Yes'), aes(x = '0-20', y = 0.35, label = paste0('Yes: ', total)), color = 'cadetblue3', family = 'Avenir', alpha = .5, size = 3, hjust = 0) +
  geom_text(data = all %>% filter(Legend == 'No'), aes(x = '0-20', y = 0.32, label = paste0('No: ', total)), color = 'coral', family = 'Avenir', alpha = .5, size = 3, hjust = 0) +
  geom_text(data = unknown_count, aes(x = '0-20', y = 0.29, label = paste0('Unknown: ', n)), color = 'orange', family = 'Avenir', alpha = .75, size = 3, hjust = 0) +
  geom_density(data = all_line, aes(x = age_cat, fill = Legend, color = Legend), alpha = .25, adjust = 3) + 
  facet_grid(~category) + theme_bw() +
  ggtitle('Age Distribution by Patient Category', subtitle = graph_caption) + xlab('Age Category') + ylab('Percentage') + scale_y_continuous(labels = scales::percent, limit = c(0, .4)) + 
  theme(text = element_text(family = 'Avenir')) + ggsave('14-Age Distribution by Category.png', width = 12)

all_print = all
names(all_print)[3:5] = c('flag', 'numerator-count', 'denominator-total')
setwd('/Users/Excenity/Documents/CHiP-LOCAL/COVID/IDPH_Data/Output/Cleaned_Data')
write.csv(all_print, 'age_distribution_byCategory_lineLevelData.csv', row.names = F)
```

Resource Utilization Distribution by Age
/*(run chunk above first*/
1. Use the data output from the previous chunk of code
2. Calculate fraction of yes and no in each age group by category
```{r echo=FALSE, message=FALSE, warning=FALSE}
all = all %>% select(category, Legend, age, n) %>% spread(key = 'Legend', value = 'n')
all$total = all$No + all$Yes
all = all %>% gather('No', 'Yes', key = 'Legend', value = 'n')
all$percentage = round(all$n / all$total,2)
all$percentage_label = paste0(as.character(all$percentage*100), '%')

subtitles = 'Unknowns removed. Patients filtered by the previous category (Hospitalized -> ICU -> Ventilator)'
caption = 'Total N for each age category labeled in red in each bar. Percentage indicates percentage for each age category' 

ggplot(all) + geom_bar(aes(x = age, y = percentage, fill = Legend), stat = 'identity', alpha = .5) +
  geom_text(data = all %>% filter(Legend == 'Yes'), aes(x = age, y = percentage - 0.05, label = percentage_label), color = 'blue', size = 4, alpha = .75, family = 'Avenir') +
  geom_text(aes(x = age, y = 0.95, label = total), color = 'Coral', alpha =.8, family = 'Avenir', size = 4) + 
  facet_grid(~category) + theme_bw() + labs(title = 'Resource Utilization Distribution by Age Category', subtitle = subtitles, caption = caption) + xlab('Age Category') + ylab('Percentage') +
  scale_y_continuous(labels = scales::percent, limit = c(0, 1)) + theme(text = element_text(family = 'Avenir')) + ggsave('15-Resource Utilization Distribution by Age.png', width = 12)

setwd('/Users/Excenity/Documents/CHiP-LOCAL/COVID/IDPH_Data/Output/Cleaned_Data')
write.csv(all, 'ResourceUtilization_byAge_lineLevelData.csv', row.names = F)
```





